---
title: "p8105_hw6_fz2352"
output: github_document
date: "2022-12-03"
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(purrr)
library(ggplot2)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 2

```{r}
homicides_df = read.csv("data/homicide-data.csv")
```

```{r}
homicides_df = 
  homicides_df %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         solved = case_when(
           disposition == "Closed without arrest" ~0,
           disposition == "Open/No arrest" ~ 0,
           disposition == "Closed by arrest" ~ 1
           ),
         victim_age = as.numeric(victim_age)) %>%
  filter(
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", " Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  )
```

```{r}
fit = 
  homicides_df %>%
  filter(city == "Baltimore") %>%
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = 'binomial')
```

```{r}
fit %>% broom::tidy()
```

```{r}
coef_sex = fit %>% broom::tidy() %>% filter(term == "victim_sexMale") %>% pull(estimate)
se_sex = coef_sex = fit %>% broom::tidy() %>% filter(term == "victim_sexMale") %>% pull(std.error)
```

The odds ratio for solving homicides comparing male to female victims keeping all other variables fixed is `r exp(coef_sex)`

```{r}
lower_ci = exp(coef_sex - se_sex)
higher_ci = exp(coef_sex + se_sex)
```

The confidence interval is `r c(lower_ci, higher_ci)`

```{r}
get_coef_sex = function(results) {
  results %>% filter(term == "victim_sexMale") %>% pull(estimate)
}

get_se_sex = function(results) {
  results %>% filter(term == "victim_sexMale") %>% pull(std.error)
}

get_CI = function(lower, higher) {
  c(lower, higher)
}
```

```{r}
fit_df = 
  homicides_df %>%
  select(city_state, solved, victim_age, victim_sex, victim_race) %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(
    models = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = 'binomial')),
    results = map(models, broom::tidy)) %>%
  select(-data, -models) %>%
  mutate(
    coef_sex = as.numeric(map(results, get_coef_sex)),
    se_sex = as.numeric(map(results, get_se_sex)),
    OR = exp(coef_sex),
    lower_ci = exp(coef_sex - 1.96 * se_sex),
    higher_ci = exp(coef_sex + 1.96 * se_sex),
    ) %>%
  select(city_state, OR, lower_ci, higher_ci)
```

```{r}
fit_df %>%
  ungroup() %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_bar(position = position_dodge(), stat = "identity") + 
  geom_errorbar(aes(ymin = lower_ci, ymax = higher_ci)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "odds ratio for solving homicides comparing male victims to female victims",
    x = "City, State",
    y = "Odds Ratio"
  )
```

In Cities from New York, NY to Tulsa, OK, homicides in which the victim is male are less likely to be resolved than those in which the victim is female. New York has the lowest OR = 0.2623978, which means homicides in which the victim is male is significantly less likely to be resolved.

In cities from Atlanta, GA to Albuquerque, NM, homicides in which the victim is male are more likely to be resolved than those in which the victim is female. Albuquerque, NM has the highest OR = 	1.7674995. which means homicides in which the victim is male is significantly more likely to be resolved.



